Comparison to other studies

### 2024-11-06 pages/other_studies.qmd
docs(other studies): table of reproduction studies, and more notes on some other papers

TODO: Consider, would there be any relevant literature related to time spent to try and get someone elses code mentioned - like how Andy mentioned there would be a max amount of time that someone in the NHS would reasonably spend troubleshooting

@@

*not sure if want to be comparing the actual proportions reproduced... or maybe do, but important to bare in mind what is being compared and what define as success... e.g. some include studies that haven't shared the code*

Starting points:

@@

    * can see completion in figure 1

@@

* @monks_computer_2023 (although overlap - look at how many of mine are from the review - some were identified from that, but some were not)

@@

And some relevant articles/discussions:

@@

    * Article then talks about interactive research objects, with everything all in one place, like "executable research articles", RMArkdown, Jupyter Book, Binder, Pangeo, NeuroLibre

@@

    * https://www.frontiersin.org/journals/neuroinformatics/articles/10.3389/fninf.2017.00069/full#B22

@@

    * https://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1005510

@@

    * https://royalsocietypublishing.org/doi/full/10.1098/rspb.2022.1113
    * Figure 1 is a nice visualisation

@@

    * https://par.nsf.gov/servlets/purl/10510561
* https://www.nature.com/articles/nn.4550

>>>>

TODO: Consider, would there be any relevant literature related to time spent to try and get someone elses code mentioned - like how Andy mentioned there would be a max amount of time that someone in the NHS would reasonably spend troubleshooting --> *struggled to find anything, so maybe just something to mention in general in discussion*

@@

## Studies that assessed reproducibility

Summary of studies that have assessed reproducibility:

| Study | Focus | N | 
| - | - | - |
| @krafczyk_learning_2021 | Articles from *Journal of Computational Physics* | 7 |
| @wood_push_2018 | Impact evaluations in low- and middle-income countries | 109 |
| @schwander_replication_2021 | Health economic obesity models | 4 |
| @laurinavichyute_share_2022 | Articles in the *Journal of Memory and Language* | 59 |
| @konkol_computational_2019 | Geoscientific articles | 31 |
| @hardwicke_analytic_2021 | Articles in *Psychological Science* | 25 |
| @henderson_reproducibility_2024 | Infectious disease models | 200 |
| @samuel_computational_2024 | Jupyter notebooks associated with publications | 3467 publications, from which 27,271 jupyter notebooks were downloaded for further analysis |

The amount they reproduce and so on isn't directly comparable as alot of variation in methods (e.g. amount of troubleshooting allowed, how decided something is reproduced or not, and so on). *not sure if want to be comparing the actual proportions reproduced... or maybe do, but important to bare in mind what is being compared and what define as success... e.g. some include studies that haven't shared the code*

@@

    * can see completion in figure 1, but focus is very much on the learnings rather than % reproduced and so on

@@

@@

## Other relevant articles for introduction and/or discussion

* @monks_computer_2023 - see summary in **introduction**

@@

    * Article then talks about interactive research objects, with everything all in one place, like "executable research articles", RMarkdown, Jupyter Book, Binder, Pangeo, NeuroLibre

@@

    * They use terms from **Goble 2016**. They then show a simple python example which they progressively modify to meet these criteria. **Really nice paper! Could be good in introduction and elsewhere?**
        * **R1: Re-runnable** (executable)
            * "it is impossible to write future-proof code... modernizing an unmaintained ten-year-old code can reveal itself to be an arduous and expensive undertaking—and precarious... more straightforward solution is to recreate the old execution environment. For this to happen however, the dependencies in terms of systems, software, and libraries must be made clear enough."
        * **R2: Repeatable** (produce the same result more than once)
            * "it often comes down to controlling the initialization of the pseudo-random number generators (RNG)." --> **importance of seeds**
        * **R3: Reproducible** (allow an investigator to reobtain published results)
            * Explicit dependencies and operating system
            * "includes pre-processing, post-processing, and plotting code"
            * good practice to include short unit tests that verify reproduction
            * code and input data and result data should all be made available
        * **R4: Reusable** (easy to use, understand and modify)
            * comments and documentation
            * "reusability can represent an expensive endeavor if undertaken as an afterthought"
            * simple things that improve reusability:
                * avoid hardcoded values or magic numbers
                * changes to code behaviour should be via modifiable parameters rather than commenting/uncommenting - so (a) conditions are recorded as parameters, and (b) can have seperate scripts to run and produce results
        * **R5: Replicable** ("act as an available reference for any ambiguity in the algorithmic descriptions of the article")
            * "replicating implies writing a new code matching the conceptual description of the article, in order to reobtain the same result"
            * whilst this relies on the article, you will inveitably have ambiguities in the article, and so "Replication efforts use the paper first, and then the reproducible code that comes along with it whenever the paper falls short of being precise enough."

@@

    * Supplements the "**Best Practices for Scientific Computing" article** by giving a minimum set of "**good enough**" things to do
    * Box 1 summarises the practices which are grouped into:
        * Data management (e.g. saving data, documenting steps, tidy data)
        * Software (eg. writing organising sharing scripts)
        * Collaboration (eg. make it easier for collaborators to understand and contribute)
        * Project organisation (eg. organise artefacts to ease discvoery and understanding)
        * Tracking changes (i.e. record how components of project change over time)
        * Manuscripts (eg. write manuscript with audit trail - so either history/change tracking, or version control)

@@

    * **Figure 1** is a nice 
    * **Barriers**
        * Knowledge barriers - unsure about process, complex or manual workflows, large data files, insecurity, do not see value
        * Reuse concerns - inappropriate use, rights, sensitive content, transient storage
        * Disincentives - scooping, lack of time, lack of incentives

@@

    * 3Rs of software enginerring: "readability (human understandable codes), resilience (fails rarely/gracefully), and reuse (can easily be used by others and can be embedded in other software)"
    * Walks through some practices... version control, software design, computer programming or coding, quality assurance, packaging and deployment, user documentation, team management, user engagement
* @eglen_toward_2017
    * Simple guidelines for code sharing: version control, persistent URLs, license, etiquette, documentation, tools, case studies, data, standards, tests, user supoprt
    * Tests - "We recommend including **test suites demonstrating that the code is producing the correct results**37. These tests can be at a low level (testing each individual function, called unit testing) or at a higher level (for example, testing that the program yields correct answers on simulated data)38." - and can link with **continuous integration** so automatically run and fail if change made to code that fails it
